EvoSwarm: An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-04-30 draft.tex
Adds clarification on why this is new refs #4

However, in the field of evolutionary algorithms, this has been a slow
realization, from the origins where Salza and Ferrucci
\cite{salza2016approach,salza2016develop} proposed an architecture
that carried evolutionary algorithms to the cloud, and which were
developed further in the next paper \cite{de2017parallel}. These
papers started to introduce cloud native aspects such as the use of
messaging queues and CoreOS as an operating system designed from the
ground up for container utilization in the area of evolutionary
algorithms. The way these containers are managed, however, is rather
classical in nature from the point of view of distributed EC: a
master-worker approach, communicated using RabbitMQ (a messaging
queue), where replicated workers perform the tasks in parallel. They
called their approach AMQPGA, inspired by the protocol, AMQP, used by
RabbitMQ, the messaging system. This classical approach has been also
followed by other authors by using other EA ``classical'' topologies
in the cloud: \cite{dziurzanski2020scalable} adapts an island model to
a container architecture, in a system that is functionally equivalent
to classical models, but with the added advantage of being easy to
deploy and run.

@@

In this section, we present the design
and a container-based implementation of the model we propose for the execution
of multi-population based algorithms. We follow the requirements outlined in
Section \ref{multi} and the general design principles of cloud-native
applications we have mentioned earlier. As a first step, we describe the general
architecture first, and then  every component in detail.

>>>>

However, in the field of evolutionary algorithms, this has been a slow
realization, from the origins where Salza and Ferrucci
\cite{salza2016approach,salza2016develop} proposed an architecture
that carried evolutionary algorithms to the cloud, and which were
developed further in their next paper \cite{de2017parallel}. These
papers started to introduce cloud native aspects such as the use of
messaging queues and CoreOS as an operating system designed from the
ground up for container utilization in the area of evolutionary
algorithms. The way these containers are managed, however, is rather
classical in nature from the point of view of distributed EC: a
master-worker approach, communicated using RabbitMQ (a messaging
queue), where replicated workers perform the tasks in parallel. They
called their approach AMQPGA, inspired by the protocol, AMQP, used by
RabbitMQ, the messaging system. This classical approach has been also
followed by other authors by using other EA ``classical'' topologies
in the cloud: \cite{dziurzanski2020scalable} adapts an island model to
a container architecture, in a system that is functionally equivalent
to classical models, but with the added advantage of being easy to
deploy and run.

@@

In this section, we present the design
and a container-based implementation of the model we propose for the execution
of multi-population based algorithms. We follow the requirements outlined in
Section \ref{multi} and the general design principles of cloud-native
applications we have mentioned earlier; our intention is to steer
clear of a direct translation of ``classical'' GA architecturs to the
cloud and design from the ground up a cloud-native method. As a first step, we describe the general
architecture first, and then  every component in detail.
